Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-05-15 LCAforActiveSonarImaging/lca.tex
...

We will show that when applied to experimental data, the weights typically chosen by a robustified MVDR yield responses that are typically symmetric and steered within a fraction of the -3dB resolution of the respective window. Then we make Kaiser windows of different types, and with varying degree of steering, that combined discretizes the MVDR solution space.

The LCA method was first introduced in clinical ultrasound imaging, where it was shown to improve image quality compared to conventional static beamforming methods \cite{Synnevag2007}.

@@

\bibliographystyle{IEEEtran}
\bibliography{references}

% 
% \input{bio/jo_inge_buskenes}
% % \input{bio/jon_petter_aasen}
% % \input{bio/carl-inge_nilsen}
% \input{bio/andreas_austeng}

>>>>

We will show that when applied to experimental data, the weights typically chosen by a robustified MVDR yield responses that are typically symmetric and steered within a fraction of the -3dB resolution of the respective window. Then we make Kaiser windows of different types, and with varying degree of steering, that combined form a discrete version of the MVDR solution space.

The LCA method was first introduced by Synnevåg et. al. in clinical ultrasound imaging, who demonstrated its ability to improve image quality compared to conventional static beamforming methods \cite{Synnevag2007}.

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
% 
% 
% \input{bio/jo_inge_buskenes}
% % \input{bio/jon_petter_aasen}
% % \input{bio/carl-inge_nilsen}
% \input{bio/andreas_austeng}
